Positive Results in Registered Reports

### 2020-01-11 manuscript/manuscript.Rmd
Adjusted formatting to make the manuscript work in journal mode. Caution: I installed the development branch of papaja to allow column-spanning tables!

header-includes:
  - \usepackage{float}
  - \usepackage{framed}
  - \usepackage{caption}
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1, footnotesize}}
  - \captionsetup[textbox]{name=Box,labelsep=period,labelfont=it}
  - \newfloat{textbox}{thp}{lop}
  - \floatname{textbox}{Box}

@@

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

lang              : "en-UK"
class             : "man"
output            : papaja::apa6_pdf
---

@@

```{r sampling, echo=FALSE, warning=FALSE, fig.cap = "(ref:sampling)", out.width = "\\textwidth"}

@@

```{r include=FALSE}
source(here("analysis", "interrater_agreement.R"))
```

@@

# Results
```{r include=FALSE}
source(here("analysis", "quantitative_analyses.R"))
```

@@

```{r mainplot, echo=FALSE, warning=FALSE, fig.width=4, fig.height=3, fig.cap="(ref:mainplot)"}
mainplot
```

@@

```{r include=FALSE}
source(here("analysis", "hypothesis_introduction_analyses.R"))
```
Finally, we analysed the language that was used to introduce or refer to hypotheses in RRs.
We were interested in whether the search phrase "test$^\ast$ the hypothes$^\ast$" used by Fanelli captured the way researchers write about hypothesis tests reasonably well. The answer is a resounding "no":
Searching the abstracts, titles, and keywords of the RR sample showed that only `r testthehypothes.RR`/`r n.RR` RRs would have been detected with this search phrase. 
To get an overview of analogous hypothesis-introduction phrases researchers used in RRs, we stripped the hypothesis quotes of RRs from all content-specific information and extracted "minimal" phrases that most distinctively indicated that a hypothesis was being described.
For example, from the hypothesis quote "(f)or Study 1, we predicted that participants reading about academic (vs. social) behaviors would show a better anagram performance" we extracted the hypothesis-introduction phrase "predicted that".

@@

```{r echo = FALSE, results = 'asis'}
apa_table(
  phrasetable.rep
  , digits = c(0, 0, 0, 0, 0, 0, 0)
  , col.names = c("", "core word(s)", "introduction phrase", "abstract", 
                  "full text", "total", "")
  , align = c("l", "l", "l", rep("r", 4))
  , caption = "(ref:table3)"
  , note = "Table contains 53 hypothesis introduction phrases from 40 Registered Reports. One additional RR had no hypothesis introduction. Thirty papers contributed one phrase each, seven contributed two each, and three contributed three each."
  , added_stub_head = "Variables"
  , col_spanners = list(`source` = c(4, 6))
  , midrules = c(6, 10, 11, 12, 29, 30, 34, 35, 36)
  , landscape = FALSE
  , font_size = "scriptsize"
  , escape = TRUE
)
```

@@

(ref:powerbaserate) Combinations of the proportion of true hypotheses and statistical power that would produce the observed positive result rates given $\alpha = 5 \%$ and no bias. Shaded areas indicate $95\%$ confidence intervals. SRs = standard reports, RRs = Registered Reports, PRR = positive result rate. The curve for all SRs (i.e, including replications; $`r printnum(prop.support.SR*100)` \%$ positive results, $N = `r n.SR`$) is not shown because it is almost identical to the one for original SRs. Plotted values were calculated using the equation $PRR = \alpha*(1-t) + (1-\beta)*t$; with $PRR =$ positive result rate, $\alpha =$ probability of obtaining a positive result when testing a false hypothesis (here fixed at .05), $1-\beta =$ probability of obtaining a positive result when testing a true hypothesis (power), and $t =$ proportion of true hypotheses; and solving for $t$ and $1-\beta$, respectively.

```{r powerbaserate, echo=FALSE, warning=FALSE, fig.width=6, fig.height=3, fig.cap="(ref:powerbaserate"}
source(here("analysis", "power_baserate_plot.R"))
power.baserate.plot
```

>>>>

header-includes:
  - \usepackage{float}
  - \usepackage{framed}
  - \usepackage{caption}
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1, small}, skip=11pt}
  - \captionsetup[textbox]{name=Box,labelsep=period,labelfont=it}
  - \newfloat{textbox}{thp}{lop}
  - \floatname{textbox}{Box}

@@

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no

lang              : "en-UK"
class             : "jou"
output            : papaja::apa6_pdf
---

@@

```{r sampling, echo=FALSE, warning=FALSE, fig.cap = "(ref:sampling)", out.width = "\\textwidth", fig.env="figure*"}

@@

```{r include=FALSE}
source(here("analysis", "01_interrater_agreement.R"))
```

@@

# Results
```{r include=FALSE}
source(here("analysis", "02_quantitative_analyses.R"))
```

@@

```{r mainplot, echo=FALSE, warning=FALSE, fig.height=5, fig.cap="(ref:mainplot)"}
mainplot
```

@@

```{r include=FALSE}
source(here("analysis", "03_hypothesis_introduction_analyses.R"))
```
Finally, we analysed the language that was used to introduce or refer to hypotheses in RRs.
We were interested in whether the search phrase "test$^\ast$ the hypothes$^\ast$" used by Fanelli captured the way researchers write about hypothesis tests reasonably well. The answer is a resounding "no":
Searching the abstracts, titles, and keywords of the RR sample showed that only `r testthehypothes.RR`/`r n.RR` RRs would have been detected with this search phrase. 
To get an overview of analogous hypothesis-introduction phrases researchers used in RRs, we stripped the hypothesis quotes of RRs from all content-specific information and extracted "minimal" phrases that most distinctively indicated that a hypothesis was being described.
For example, from the hypothesis quote "(f)or Study 1, we predicted that participants reading about academic (vs. social) behaviors would show a better anagram performance" we extracted the hypothesis-introduction phrase "predicted that".

@@

```{r echo = FALSE, results = 'asis'}
apa_table(
  phrasetable.rep
  , digits = c(0, 0, 0, 0, 0, 0, 0)
  , col.names = c("", "core word(s)", "introduction phrase", "abstract", 
                  "full text", "total", "")
  , align = c("l", "l", "l", rep("r", 4))
  , caption = "(ref:table3)"
  , note = "Table contains 53 hypothesis introduction phrases from 40 Registered Reports. One additional RR had no hypothesis introduction. Thirty papers contributed one phrase each, seven contributed two each, and three contributed three each."
  , added_stub_head = "Variables"
  , col_spanners = list(`source` = c(4, 6))
  , midrules = c(6, 10, 11, 12, 29, 30, 34, 35, 36)
  , landscape = FALSE
  , font_size = "footnotesize"
  , escape = TRUE
)
```

@@

(ref:powerbaserate) Combinations of the proportion of true hypotheses and statistical power that would produce the observed positive result rates given $\alpha = 5 \%$ and no bias. Shaded areas indicate $95\%$ confidence intervals. SRs = standard reports, RRs = Registered Reports. The curve for all SRs (i.e, including replications; $`r printnum(prop.support.SR*100)` \%$ positive results, $N = `r n.SR`$) is not shown because it is almost identical to the one for original SRs. Plotted values were calculated using the equation $PRR = \alpha*(1-t) + (1-\beta)*t$; with $PRR =$ positive result rate, $\alpha =$ probability of obtaining a positive result when testing a false hypothesis (here fixed at .05), $1-\beta =$ probability of obtaining a positive result when testing a true hypothesis (power), and $t =$ proportion of true hypotheses; and solving for $t$ and $1-\beta$, respectively.

```{r powerbaserate, echo=FALSE, fig.width=5, fig.height=3, fig.align='center', warning=FALSE, fig.cap="(ref:powerbaserate)",   out.width = "0.6\\textwidth", fig.env="figure*"}
source(here("analysis", "04_power_baserate_plot.R"))
power.baserate.plot
```
